<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{Using registries to maintain state between R sessions}
-->

```{r, echo = FALSE, message = FALSE}
library(director)
```

# Using registries to maintain state between R sessions

Frequently, there is a need to maintain state between consecutive R sessions without
polluting the local project with temporary or configuration-related files. 

`director` aims to solve this problem by providing a `registry`, a simple wrapper
around reading and writing to a directory that takes cares of checking for non-existent paths.

A registry should be used only internally by a project to store data it needs to maintain
across R sessions (or amongst different R sessions) and should not be exposed to the user.
This is because the keys you choose to store values under are purely convention, and you
do not want to give someone the ability to overwrite them.

```{r}
r <- registry$new(file.path(dirname(tempfile()), '.registry'))
# You don't have to use .registry, but making the directory hidden is preferable
# as it is for internal use only.

r$set('some/key', list('some', 5, 'value'))
value <- r$get('some/key') # value is now the above list.
print(value)
```

You can perform complicated logic with this.

```{r}
projects <- list(proj1 = list(config_key1 = 'config_value1', config_key2 = 'config_value2'),
                 proj2 = list(config_key1 = 'settings_value1', config_key2 = 'settings_value2'))
for (name in names(projects)) r$set(file.path(name, 'config'), projects[[name]])
print(sapply(names(projects), function(name) r$get(file.path(name, 'config'))$config_key1))
```
